### 2016-05-13 paper/paper.tex
add some conclusion, fixup references, more detail on tls 1.3 and ssh

Although the proof-of-work used in Bitcoin gives it resistance to sybil attacks,
the amount of computational effort carried out collectively by its miners does
not contribute to any problems besides securing the currency from attack.
Indeed, this computational effort is substantial: As of 2016, miners
collectively perform roughly $10^{18}$ (or about $2^{60}$) hashes every
second~\cite{blockchain}.

@@

\emph{Contributions}
\begin{itemize}
\item Propose a novel conceptual cryptocurrency, DDoSCoin, whose proof-of-work
incentives miners to participate in a DDoS attack, and prove they have done so.
\item Describe a way for target victims to be chosen by consensus.
\item Implement our proof-of-work function and evaluate its performance.
\item Discuss and estimate the impact such a cryptocurrency would have if
deployed, and outline defenses.
\end{itemize}

Section blah does blah, and Section blat describes blat.

@@

Ethereum
Permacoin
Primecoin
Other interesting proofs-of-work?

Botnet-as-a-service

@@

\subsection{Cryptocurrency}

\FigTx

@@

The miner initiates a TLSv1.2 connection with the victim server, using the
\texttt{client\_random}, and choosing a set of cipher suites that will ensure
the server will send a server key exchange message. This includes ephemeral
Diffie-Hellman (DHE), and ephemeral elliptic curve Diffie-Hellman (ECDHE). We
note that for the default cipher suite list sent by Google Chrome, over 94\%
of TLS 1.2 servers in the Alexa top million choose a cipher suite with a server key exchange
message~\cite{censys}, compatible with DDoSCoin.
% https://censys.io/domain/report?q=443.https.tls.version%3A%22TLSv1.2%22&field=443.https.tls.cipher_suite.name&max_buckets=

@@

DDoSCoin is incompatible with earlier TLS (or even SSL) versions because the
server key exchange signature does not include the \texttt{client\_random}, or
any client-provided values. If we were to try to base a proof-of-work off of an
earlier version of TLS, the only value that provably comes from the server (i.e.
is signed by a key tied to the victim's identity) does not contain any
comittments from the client about the previous block, or what transactions
should be included in the block. If we were to accept blocks where there was
only a server signature that met some target difficulty, any miner could steal
another miner's found block (and the contained block reward) by changing the
transactions and forwarding the block.

@@

This interesting property gives rise to an observation that with respect to
clients, the contents of TLS connections are \emph{deniable}. That is, it is not
possible for a client to record a TLS connection, including its chosen secrets,
and report this to a third party in a way that cryptographically proves what the
server says. This property has been accomplished in different more efficient ways in various
secure messaging protocols such as Off-the-Record (OTR)~\cite{otr}.

Besides TLS 1.2, there are other cryptographic protocols that have the feature
of the server signing a client-chosen value. For example, SSH ... \TK

Although not yet implemented, the TLS 1.3 proposal appears to also have ... \TK

@@

@@

@@

>>>>

Although the proof-of-work used in Bitcoin gives it resistance to sybil attacks,
the amount of computational effort carried out collectively by its miners does
not contribute to any problems besides securing the currency from attack.
Indeed, this computational effort is substantial: As of 2016, miners
collectively perform roughly $10^{18}$ (or about $2^{60}$) hashes every
second~\cite{blockchain-hashrate}.

@@

\emph{Contributions}
\begin{itemize}
\item Propose a novel conceptual cryptocurrency, DDoSCoin, whose proof-of-work
incentives miners to participate in a DDoS attack, and prove they have done so.
\item Describe a way for target victims to be chosen by consensus.
\item Implement our proof-of-work function and evaluate its performance.
\item Discuss and estimate the impact such a cryptocurrency would have if
deployed, and outline defenses.
\end{itemize}
%TODO: remove this last one?

%Section blah does blah, and Section blat describes blat.

@@

Many alternate cryptocurrency protocols (alt-coins) have been proposed since the
creation of Bitcoin. Although none have yet eclipsed the popularity of Bitcoin,
many alt-coins have interesting innovations, often in the form of alternate
proof-of-work. For example, Litecoin uses scrypt in place of SHA256 in its
proof-of-work, with the intention of being ``ASIC-resistant'' in order to allow
anyone to mine competatively with only a CPU~\cite{litecoin}.

Permacoin is a proposed alt-coin that uses a novel
\emph{proof-of-storage}~\cite{permacoin}.  Rather than waste computational
resources solving a useless proof-of-work puzzle (as in Bitcoin), miners are
instead incentivzed to store parts of a large agreed-upon file. In order to be
competitive in Permacoin, miners prove that they can retreive an assigned
portion of the file.

In Primecoin, miners search for special chains of prime
numbers~\cite{primecoin}. Although Primecoin has found several large Cunningham
and bi-twin chains, it remains unclear if such primes have any practical use.

Although Bitcoin uses a scripting language for transactions (see
Section~\ref{sec:scripting}), the allowed operations are very
limited~\cite{bitcoin-paper}. Ethereum allows transactions to be
\emph{programmable contracts}, whereby a programmer can specify in a custom
scripting language arbitrary logic, including conditional payments or
fee-collection. While the Ethereum Virtual Machine (EVM) that executes these
contracts does not provide external network access to the scripts, it could
still be used to implement some parts of DDoSCoin. For example, it is possible
to create an Ethereum contract that pays a bounty to anyone that can provide a
proof-of-DDoS for a specified target. This would effectively accomplish the same
outcome as PAY\_TO\_DDOS (described in Section~\ref{sec:pay-to-ddos}), and
implementing DDoSCoin's proof-of-DDoS verification.

%Other interesting proofs-of-work?  Botnet-as-a-service?

@@

\subsection{Cryptocurrency}
\label{sec:scripting}
\FigTx

@@

The miner initiates a TLS version 1.2~\cite{rfc5246} connection with the victim
server, using the \texttt{client\_random}, and choosing a set of cipher suites
that will ensure the server will send a server key exchange message. This
includes ephemeral Diffie-Hellman (DHE), and ephemeral elliptic curve
Diffie-Hellman (ECDHE). We note that for the default cipher suite list sent by
Google Chrome, over 94\% of TLS 1.2 servers in the Alexa top million choose a
cipher suite with a server key exchange message~\cite{censys}, compatible with
DDoSCoin.
% https://censys.io/domain/report?q=443.https.tls.version%3A%22TLSv1.2%22&field=443.https.tls.cipher_suite.name&max_buckets=

@@

DDoSCoin is incompatible with earlier TLS (or even SSL) versions because the
server key exchange signature does not include the \texttt{client\_random}, or
any client-provided values. In earlier versions, the only value that provably comes from the server (i.e.
is signed by a key tied to the victim's identity) does not contain any
comittments from the client about the previous block, or what transactions
should be included in the block. If we were to accept blocks where there was
only a server signature that met some target difficulty, any miner could steal
another miner's found block (and the contained block reward) by changing the
transactions and forwarding the block.

@@

This interesting property gives rise to an observation that with respect to
clients, the contents of TLS connections are \emph{deniable}. That is, it is not
possible for a client to record a TLS connection (including its chosen secrets)
and report this to a third party in a way that cryptographically proves what the
server says. This property has been accomplished in different more efficient ways in various
secure messaging protocols such as Off-the-Record (OTR)~\cite{otr}.

Besides TLS 1.2, there are other cryptographic protocols that include the server
signing a client-chosen value. For example, the SSH protocol key exchange
involves the server signing a hash over the previous handshake messages,
including the client-provided identification (version) string, and
Diffie-Hellman public value~\cite{rfc4253}. Either of these fields could be used
to encode the necessary commitments (previous block, merkle root, and nonce)
used in DDoSCoin.  However, SSH server identities are generally not signed by a
trusted party, making verification that a miner has communicated with a
particular server more complicated.  Nonetheless, identities in an SSH-based
DDoSCoin could be based off of the server's host key, rather than a domain in a
CA-signed certificate.

Although not yet implemented, the current TLS 1.3 proposal appears to also have the
property of the server signing messages sent by the client. In particular, the
Certificate Verify message includes a signature from the server over essentially
all prior handshake messages, including the Client Hello that contains the
\texttt{client\_random}. Thus, DDoSCoin could be used against TLS 1.3
servers with only minor modifications.

@@

\subsection{Implementation}

To evaluate its performance, we implement our proof-of-DDoS function in 570
lines of C. Our mining code uses libevent~\cite{libevent} and
OpenSSL~\cite{openssl}.

From wifi: 100 concurrent conns, 10k connections total in 53 seconds, 500KB/s
roughly (no CPU load)

TODO: measure from CU...or to a local server?

@@

\subsection{Defenses}

There are several methods victim websites can use to defend themselves from
DDoSCoin miners. First, websites can simply disable TLS 1.2 entirely, and only
support earlier versions such as TLS 1.0~\cite{rfc2246} and TLS
1.1~\cite{rfc4346}. While older versions of
TLSv1.0 clients may still be vulnerable to the BEAST attack~\cite{beast}, most
modern clients have mitigations for this attack, and it likely remains the
safest short-term defense against DDoSCoin. The downside of disabling support
for TLSv1.2 is losing the ability to negotiate authenticated encryption cipher
modes with clients, which may decrease performance of implementations that have
hardware acceleration for such modes.

Alternatively, web servers can disable cipher modes that involve signatures from
the server. This would remove support for forward secure cipher suites, meaning
that as long as the server's private key is accessible, any previously recorded
TLS connections can be decrypted. We note that the current drafts of TLSv1.3
propose to remove non-forward secure cipher suites entirely, possibly making it
more difficult to defend against DDoSCoin in TLSv1.3.

Websites could also attempt to thwart DDoSCoin by participating in the mining
themselves. Because the victim website will have local access to its private
key, they will have an advantage over remote clients. With this advantage, the
victim might be able to mine enough DDoSCoins to mint a proof-of-stake block
that removes itself from the list.

Finally, websites could attempt to go after mining operations legally:
Publishing a proof-of-DDoS block in the DDoSCoin blockchain may reveal intent to
bring down a service for financial profit. If the victim webserver is able to
log the traffic they receive, they can discover the IP address of the party
given a published proof-of-DDoS block. However, as many attackers may use proxies,
botnets, or bullet-proof hosting to carry out their attacks, finding an
attacker's IP address may not be sufficient for legal action.

@@

In this paper, we have presented a proof-of-DDoS, whereby cryptocurrency miners
can prove their involvement in sending a large amount of requests to a specified
victim webserver. Proof-of-DDoS can be used to replace proof-of-work in a
cryptocurrency setting, provided that there is consensus around what victims are
valid targets. Our conceptual alt-coin, DDoSCoin, provides such a concensus
through two mechanisms: PAY\_TO\_DDOS, whereby a bounty can be set for DDoSing a
given victim domain, and proof-of-stake updates to the list of valid victims.

The relatively-short history of cryptocurrency is an exciting one, litered with
mystery
